Fig3

### 2020-05-21 analysis/figure-3.Rmd
better fig 3

pca1f <- subsetmakepca("pituitary", alllevels, "female")	
pca2f <- makefvizdf("pituitary", alllevels, "female")

pca1m <- subsetmakepca("pituitary", alllevels, "male")	
pca2m <- makefvizdf("pituitary", alllevels, "male")

pca1 <- subsetmakepca("pituitary", alllevels, sexlevels)	
pca2 <- makefvizdf("pituitary", alllevels, sexlevels)	
```

@@

```{r}
# candidate counts for boxplots
candidatevsd <- read_csv("../results/06_candidatevsd.csv") %>%
  mutate(treatment = factor(treatment)) %>%
  mutate(tissue = factor(tissue, levels = tissuelevel),
        treatment = factor(treatment, levels = alllevels)) %>%
  drop_na()

@@

# list of pvalue and DEGs
allDEG <- read_csv("../results/06_allDEG.csv") 
allDEG2 <- allDEG

# candidate genes from GO and literature
parentalcaregenes <- read_csv("../metadata/03_parentalcaregenes.csv") %>% pull(gene)

@@

eggchickdf <- allDEG %>%
  filter(comparison != "lo_hi")  %>%
  arrange(padj)

@@

## for correlations
pithilo <- makecorrdf("female", "pituitary", hilogenes)
piteggchick <- makecorrdf("female", "pituitary", eggchickgenes)
pitWGCNA <- makecorrdf("female", "pituitary", WGCNAgenes[1:20])
parentalcare <- makecorrdf("female", "pituitary", parentalcaregenes[1:20])
```

@@

a1 <- plotpc12(pca1, pca2, pca1$treatment, allcolors, "Pituitary gene expression", " ")   
a2 <- plotprolactin(PRLpit, PRLpit$counts, "PRL", " ") + 
  theme(axis.text.x = element_text(angle = 25))  +
  theme(legend.position = c(0.8,0.2)) + 
  guides(fill = FALSE) 
a <- plot_grid(a1,a2, labels = c("A"), label_size = 8, rel_widths = c(1,1.1))

b1 <- png::readPNG("../figures/images/fig_fig3b.png")
b1 <- ggdraw() +  draw_image(b1, scale = 1)
b2 <- makenewbargraph("pituitary", "female","eggs_chicks", 0, 400) + labs(subtitle = "female")  + labs(title = " ")  
b3 <- makenewbargraph("pituitary", "male", "eggs_chicks", 0, 400)  + labs(subtitle = "male")  + labs(title = " ") +
  theme(axis.title.y = element_blank(), axis.ticks.y = element_blank(), 
        axis.text.y = element_blank(), axis.line.y = element_blank())
b4 <- makenewbargraph("pituitary", "male", "lo_hi", 0, 4000) 
b5 <- makenewbargraph("pituitary", "female", "lo_hi", 0, 4000)   + 
  theme(axis.title.y = element_blank(), axis.ticks.y = element_blank(), 
        axis.text.y = element_blank(), axis.line.y = element_blank())
b25 <- plot_grid(b2,b3,b4,b5, nrow = 2, rel_widths = c(1.2,1), rel_heights = c(1.2,1))
b6 <-  plottopDEGs(eggchickdf, "female", "#3A80B9", "LFC eggs vs. chicks", "Top 10 female DEGs") + labs(title = " ")
b7 <-  plottopDEGs(hilodf, "male", "#3A80B9", "LFC eggs vs. chicks", "Top 10 male DEGs") + labs(title = " ")
b8 <-  plottopDEGs(hilodf, "female", "#19757A", "LFC lo vs. hi PRL", NULL)
b9 <-  plottopDEGs(hilodf, "male", "#19757A", "LFC lo vs. hi PRL", NULL)
b15 <- plot_grid(b1,b25,nrow = 1, rel_widths = c(1.2,1))
b69 <- plot_grid(b6,b7,b8,b9, align = "v" , rel_heights = c(1.2,1))
b <- plot_grid(b15,b69, labels = c("B"), label_size = 8, rel_widths = c(1.2,1))

c1 <- plotcorrplot(piteggchick, NULL) + theme(legend.position = "none") + labs(subtitle = "Top 20 eggs vs. chicks DEGs")
c2 <- plotcorrplot(pithilo, NULL) + theme(legend.position = "none") + labs(subtitle = "Top 20 lo vs. PRL DEGs") 
d <- plotcorrplot(pitWGCNA, NULL) + theme(legend.position = "none") + labs(subtitle = "20 genes from WGCNA module with PRL") + theme(legend.position = "right")
cd <- plot_grid(c1,c2,d, nrow = 1, align = "h", labels = c("C", "", "D"), label_size = 8, rel_widths = c(1,1,1.3))

fig3 <- plot_grid(a, b, cd, nrow = 3, rel_heights = c(1.2,2,1.8))
fig3

>>>>

pca1f <- subsetmakepca("pituitary", charlevelsnocontrol, "female")	
pca2f <- makefvizdf("pituitary", charlevelsnocontrol, "female")

pca1m <- subsetmakepca("pituitary", charlevelsnocontrol, "male")	
pca2m <- makefvizdf("pituitary", charlevelsnocontrol, "male")

pca1 <- subsetmakepca("pituitary", charlevelsnocontrol, sexlevels)	
pca2 <- makefvizdf("pituitary", charlevelsnocontrol, sexlevels)	
```

@@

```{r}
# candidate counts for boxplots
candidatevsd <- read_csv("../results/06_candidatevsd.csv") %>%
  mutate(treatment = factor(treatment)) %>%
  mutate(tissue = factor(tissue, levels = tissuelevel),
        treatment = factor(treatment, levels = charlevelsnocontrol)) %>%
  drop_na()

@@

# list of pvalue and DEGs
allDEG <- read_csv("../results/06_allDEG.csv")  %>%
  mutate(direction = factor(direction, levels = hypothesislevels))

# candidate genes from GO and literature
parentalcaregenes <- read_csv("../metadata/03_parentalcaregenes.csv") %>% 
  distinct(literature)  %>% drop_na() %>% pull(literature)

@@

eggchickdf <- allDEG %>%
  filter(!comparison %in% c("lo_hi", "nest_eggs", "nest_chicks"))  %>%
  arrange(padj)

@@

## for correlations
pithilo <- makecorrdf("female", "pituitary", hilogenes)
pitWGCNA <- makecorrdf("female", "pituitary", WGCNAgenes[1:20])

## for scatter correlation

candidatevsdwide <- candidatevsd  %>%
    pivot_wider(names_from = gene, values_from = counts) 
pitwide <- subsetcandidatevsdwide(sexlevels, "pituitary")

@@

a1 <- plotpc12(pca1, pca2, pca1$treatment, allcolors, "Pituitary gene expression", NULL)   
a2 <- plotprolactin(PRLpit, PRLpit$counts, "PRL", NULL) + 
  theme(axis.text.x = element_text(angle = 25))  +
  facet_wrap(~sex)
a <- plot_grid(a1,a2, labels = c("A", "B"), label_size = 8, rel_widths = c(1,1))

b1 <- png::readPNG("../figures/images/fig_fig3b.png")
b1 <- ggdraw() +  draw_image(b1, scale = 1)
b2 <- makenewbargraph("pituitary", "female","eggs_chicks", 0, 4000) + labs(subtitle = "female")  + labs(title = " ") +
  scale_x_discrete(labels = "eggs vs. chicks")
b3 <- makenewbargraph("pituitary", "male", "eggs_chicks", 0, 4000)  + labs(subtitle = "male")  + labs(title = " ") +
  theme(axis.title.y = element_blank(), axis.ticks.y = element_blank(), 
        axis.text.y = element_blank(), axis.line.y = element_blank()) +
  scale_x_discrete(labels = "eggs vs. chicks")
b4 <- makenewbargraph("pituitary", "male", "lo_hi", 0, 4000)  +
  scale_x_discrete(labels = "lo vs. hi PRL")
b5 <- makenewbargraph("pituitary", "female", "lo_hi", 0, 4000)   + 
  theme(axis.title.y = element_blank(), axis.ticks.y = element_blank(), 
        axis.text.y = element_blank(), axis.line.y = element_blank()) +
  scale_x_discrete(labels = "lo vs. hi PRL")
b25 <- plot_grid(b2,b3,b4,b5, nrow = 2, rel_widths = c(1.2,1), rel_heights = c(1.2,1))

b6 <-  plottopDEGs(eggchickdf, "female",  "LFC eggs vs. chicks", "Top 10 female DEGs") + labs(title = " ")
b7 <-  plottopDEGs(eggchickdf, "male",  "LFC eggs vs. chicks", "Top 10 male DEGs") + labs(title = " ")
b8 <-  plottopDEGs(hilodf, "female",  "LFC lo vs. hi PRL", NULL)
b9 <-  plottopDEGs(hilodf, "male",  "LFC lo vs. hi PRL", NULL)
b15 <- plot_grid(b1,b25,nrow = 1, rel_widths = c(1.2,1))
b69 <- plot_grid(b6,b7,b8,b9, align = "v" , rel_heights = c(1.2,1))
b <- plot_grid(b15,b69, labels = c("C"), label_size = 8, rel_widths = c(1.2,1))

c1 <- plotcorrplot(pithilo, NULL) + theme(legend.position = "none") + labs(subtitle = "Top 20 lo vs. hi PRL DEGs") 
c2 <- plotcorrplot(pitWGCNA, NULL) + theme(legend.position = "none") + labs(subtitle = "20 genes from WGCNA module with PRL") + theme(legend.position = "right")
c3 <- candidateboxplot("pituitary", c("KPNA2"), sexlevels)
c4 <- candidateboxplot("pituitary", c("CDK1"), sexlevels) + 
  theme(axis.text.x = element_text(angle = 45, hjust =1), strip.text = element_blank())  + labs(x = " ")
c34 <- plot_grid(c3,c4, nrow = 2, rel_heights = c(1,1.2))

c <- plot_grid(c1,c2,c34, nrow = 1, labels = c("D", "", "E"), label_size = 8, rel_widths = c(1.1,1.4,1))

fig3 <- plot_grid(a, b, c, nrow = 3, rel_heights = c(1.2,2,1.8))
fig3
